{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Stil on first slides of GPM

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> AUG: We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        slight difference in the profile of parallel connection
        length. This required operation at unusual low toroidal field
        (up to 0.8T)
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: The difference in target pressure similar
        to AUG behavior
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<6|only@6> TCV: This tendency is not observed for TCV where
        profiles seem resilient to modification of Bt.

      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

>>>>

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> AUG: We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        slight difference in the profile of parallel connection
        length. This required operation at unusual low toroidal field
        (up to 0.8T)
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: The difference in target pressure similar
        to AUG behavior
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
      \item<6|only@6> TCV: This tendency is not observed for TCV where
        profiles seem resilient to modification of Bt even though we
        reached pretty high value of $\Lambda_{div}$ all along the profile.
      \item<7|only@7> TCV: This is due to the fact that we can't
        observed during the density ramp any signature of rollover or detachment,
        whereas upstream profile modification at TCV are only observed
        well after rollover
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}
